Manuscript Figures for Genome Biology

### 2018-05-28 manuscript_figures/manuscript_figures.Rmd
Add layer to method rank heatmaps with prop total possible

Fig4.rowOrder <- levels(plotMethodRanks(objects, colLabels = casestudy, alpha = alpha,
                            tableOnly = TRUE)$method)
Fig4 <- plotMethodRanks(objects, colLabels = casestudy, alpha = alpha)
Fig4

@@

Create another panel with heatmap of yeast simulation results.

@@

pfdr <- plotMethodRanks(objs, 
                colLabels = c("sim", "sim"), 
                alpha = alpha, xlab = "Comparison",
                fill = "FDR",
                rowOrder = Fig4.rowOrder) +
          scale_fill_gradient2(high = "red", 
                         mid = "white", 
                         low = "blue", 
                         midpoint = alpha)

ptpr <- plotMethodRanks(objs, 
                colLabels = c("sim", "sim"), 
                alpha = alpha, xlab = "Comparison",
                fill = "TPR",
                colorLow = "blue", 
                colorHigh = "white",
                rowOrder = Fig4.rowOrder)

@@

```{r}
# by covariate
wcs <- which(grepl("GWAS", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-"), 
                      function(x) x[2]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Covariate",
                excludeMethods = NULL, Nlabel = FALSE) + 
  ggtitle("GWAS")
ggsave(file.path(outdir, "FigureS1.pdf"), width=4, height=4)
```

@@

```{r}
#by dataset
wcs <- which(grepl("GSEA", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Dataset", Nlabel = FALSE) + 
  ggtitle("GSEA")
ggsave(file.path(outdir, "FigureS2.pdf"), width=4, height=4)
```

@@

```{r}
wcs <- which(grepl("ChIPseq", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Dataset", Nlabel = FALSE) + 
  ggtitle("ChIP-Seq")
ggsave(file.path(outdir, "FigureS3.pdf"), width=5, height=4)
```

### RNA-seq
```{r}
# by dataset
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("polyester|yeast"), dataset) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Dataset", 
                excludeMethods = NULL, Nlabel = FALSE) + 
  ggtitle("RNA-seq")
ggsave(file.path(outdir, "FigureS4.pdf"), width=4, height=4)
```

@@

# by dataset
pa <- plotMethodRanks(objs, colLabels = ds, alpha = alpha, xlab = "Dataset") + 
  ggtitle("scRNA-seq")

# by method
pb <- plotMethodRanks(objs, colLabels = meth, alpha = alpha, xlab = "Method") + 
  ggtitle("scRNA-seq")

# by covariate
pc <- plotMethodRanks(objs, colLabels = cv, alpha = alpha, xlab = "Covariate") + 
  ggtitle("scRNA-seq")

@@

```{r}
# by dataset, excluding otu when genus is available
# excluding log-ubiquity
# excluding enigma-so4 (no discoveries)
wcs <- which(grepl("microbiome", casestudy) & 
              !(grepl(c("goodrich|papa"), dataset) & 
              grepl(c("otu"), dataset)) &
              !grepl("log-ubiquity", dataset) &
              !grepl("so4", dataset) &
              !grepl("baxter", dataset) )
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Dataset", Nlabel = FALSE) + 
  ggtitle("Microbiome")
ggsave(file.path(outdir, "FigureS6.pdf"), width=7.5, height=4)
```

>>>>

Fig4.rowOrder <- levels(plotMethodRanks(objects, colLabels = casestudy, alpha = alpha,
                            tableOnly = TRUE)$method)
Fig4 <- plotMethodRanks(objects, colLabels = casestudy, alpha = alpha,
                        annotate = "propPossible")
Fig4

@@

Create more panels with heatmaps of yeast simulation results.

@@

pfdr <- plotMethodRanks(objs, 
                colLabels = c("sim", "sim"), 
                alpha = alpha, xlab = "Comparison",
                fill = "FDR",
                rowOrder = Fig4.rowOrder, 
                annotate = "FDR") +
          scale_fill_gradient2(high = "red", 
                         mid = "white", 
                         low = "blue", 
                         midpoint = alpha)

ptpr <- plotMethodRanks(objs, 
                colLabels = c("sim", "sim"), 
                alpha = alpha, xlab = "Comparison",
                fill = "TPR",
                colorLow = "blue", 
                colorHigh = "white",
                rowOrder = Fig4.rowOrder,
                annotate = "TPR")

@@

```{r}
# by covariate
wcs <- which(grepl("GWAS", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-"), 
                      function(x) x[2]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Covariate",
                excludeMethods = NULL, Nlabel = FALSE, annotate = "propPossible") + 
  ggtitle("GWAS")
ggsave(file.path(outdir, "FigureS1.pdf"), width=4, height=4)
```

@@

```{r}
#by dataset
wcs <- which(grepl("GSEA", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Dataset", 
                Nlabel = FALSE, annotate = "propPossible") + 
  ggtitle("GSEA")
ggsave(file.path(outdir, "FigureS2.pdf"), width=4, height=4)
```

@@

```{r}
wcs <- which(grepl("ChIPseq", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Dataset", 
                Nlabel = FALSE, annotate = "propPossible") + 
  ggtitle("ChIP-Seq")
ggsave(file.path(outdir, "FigureS3.pdf"), width=5, height=4)
```

### RNA-seq
```{r}
# by dataset
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("polyester|yeast"), dataset) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Dataset", 
                excludeMethods = NULL, Nlabel = FALSE, annotate = "propPossible") + 
  ggtitle("RNA-seq")
ggsave(file.path(outdir, "FigureS4.pdf"), width=4, height=4)
```

@@

# by dataset
pa <- plotMethodRanks(objs, colLabels = ds, alpha = alpha, 
                      xlab = "Dataset", annotate = "propPossible") + 
  ggtitle("scRNA-seq")

# by method
pb <- plotMethodRanks(objs, colLabels = meth, alpha = alpha,
                      xlab = "Method", annotate = "propPossible") + 
  ggtitle("scRNA-seq")

# by covariate
pc <- plotMethodRanks(objs, colLabels = cv, alpha = alpha,
                      xlab = "Covariate", annotate = "propPossible") + 
  ggtitle("scRNA-seq")

@@

```{r}
# by dataset, excluding otu when genus is available
# excluding log-ubiquity
# excluding enigma-so4 (no discoveries)
wcs <- which(grepl("microbiome", casestudy) & 
              !(grepl(c("goodrich|papa"), dataset) & 
              grepl(c("otu"), dataset)) &
              !grepl("log-ubiquity", dataset) &
              !grepl("so4", dataset) &
              !grepl("baxter", dataset) )
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Dataset", 
                Nlabel = FALSE, annotate = "propPossible") + 
  ggtitle("Microbiome")
ggsave(file.path(outdir, "FigureS6.pdf"), width=7.5, height=4)
```
